Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex
Minor content revisions, add references.
update

KOI

@@

EOD

MICROLENSING, IMAGING, TIMING and ASTROMETRY

@@

DIST

@@

MASSS

@@

@@

S - changed to SHK; What's the source for SHK and RHK? Still discovery
paper and Butler 2006?

@@

KEPID\dotfill & & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & & KOI object number & \nodata \\

@@

DIST\dotfill & & Distance to host star based on parallax in parsecs & -UPPER, etc. \\

@@

MASS\dotfill & & Mass of planet in \mjup & -UPPER, etc. \\
SEP\dotfill & & Separation between host star and planet in AU & -UPPER, etc. \\

@@

BIGOM\dotfill & & Longitude of ascending node in degrees & -UPPER, etc. \\

@@

AR\dotfill & & $(a/R_*)$ & -UPPER, etc. \\

@@

DR\dotfill & & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & & $(R_p/R_*)$ & -UPPER, etc. \\

@@

SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$

@@

SEDEPTHKP\dotfill & & Secondary eclipse depth in the

@@

SEDEPTH36\dotfill & & Secondary eclipse depth in

@@

SEDEPTH45\dotfill & & Secondary eclipse depth in

@@

SEDEPTH58\dotfill & & Secondary eclipse depth in

@@

SEDEPTH80\dotfill & & Secondary eclipse depth in

@@

SET\dotfill & & ZZZ Epoch of secondary eclipse center in

@@

RSTAR\dotfill & & Radius of host star in solar radii & -UPPER, etc. \\

@@

RHOSTAR\dotfill & & Density of host star & -UPPER, etc. \\

@@

KP\dotfill & & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & & Source of most of the spectroscopic parameters & SPECURL \\

>>>>

KOI:

@@

EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets"  on exoplanets.org

@@

DIST: actually, DIST is not added since Wright 2011 (It was just left out)

@@

MASS: Previously, we only reported the minimum mass (MSINI) of the planets. We now report mass of the planet in the unit of Jupiter mass. If a planet is discovered by transit, the planet mass is given by the literature. However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination. MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to``Set to MSINI; I unknown"

@@

LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009.

@@

S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
paper and Butler 2006?

@@

KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\

@@

DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\

@@

MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\

@@

BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\

@@

AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\

@@

DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\

@@

SEDEPTHJ\dotfill & Double & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & Double & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & Double & Secondary eclipse depth in $K_S$

@@

SEDEPTHKP\dotfill & Double & Secondary eclipse depth in the

@@

SEDEPTH36\dotfill & Double & Secondary eclipse depth in

@@

SEDEPTH45\dotfill & Double  & Secondary eclipse depth in

@@

SEDEPTH58\dotfill & Double  & Secondary eclipse depth in

@@

SEDEPTH80\dotfill & Double & Secondary eclipse depth in

@@

SET\dotfill & Double & ZZZ Epoch of secondary eclipse center in

@@

RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\

@@

RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\

@@

KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
